\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[english,russian]{babel}
\usepackage{cite}

\begin{document}

\title{Список публикаций (без препринтов)}
\author{П.В. Осиненко}
\date{}
\maketitle

\begin{enumerate}

\item P.V. Osinenko, M. Geissler, T. Herlitzius. A method of optimal traction control for farm tractors with feedback of drive torque. \textit{Biosystems engineering}, 129, 20-33, 2015. (78 цитирований)

\item \textbf{P. Osinenko}, S. Streif. Optimal traction control for heavy-duty vehicles. \textit{Control Engineering Practice}, 69, 99-111, 2017. (33 цитирования)

\item \textbf{P. Osinenko}, D. Dobriborsci, W. Aumer. Reinforcement learning with guarantees: a review. \textit{IFAC-PapersOnLine}, 55 (15), 123-128, 2022. (29 цитирований)

\item \textbf{P. Osinenko}, K. Biegert, R.J. McCormick, T. Göhrt, G. Devadze, J. Streif, et al. Application of non-destructive sensors and big data analysis to predict physiological storage disorders and fruit firmness in 'Braeburn'apples. \textit{Computers and Electronics in Agriculture}, 183, 106015, 2021. (29 цитирований)

\item S. Ibrahim, M. Mostafa, A. Jnadi, H. Salloum, \textbf{P. Osinenko}. Comprehensive overview of reward engineering and shaping in advancing reinforcement learning applications. \textit{IEEE Access}, 2024. (27 цитирований)

\item T. Bögel, \textbf{P. Osinenko}, T. Herlitzius. Assessment of soil roughness after tillage using spectral analysis. \textit{Soil and Tillage Research}, 159, 73-82, 2016. (18 цитирований)

\item \textbf{P. Osinenko}, L. Beckenbach, T. Göhrt, S. Streif. A reinforcement learning method with closed-loop stability guarantee. \textit{IFAC-PapersOnLine}, 53 (2), 8043-8048, 2020. (16 цитирований)

\item L. Beckenbach, \textbf{P. Osinenko}, S. Streif. A Q-learning predictive control scheme with guaranteed stability. \textit{European Journal of Control}, 56, 167-178, 2020. (15 цитирований)

\item L. Beckenbach, \textbf{P. Osinenko}, T. Göhrt, S. Streif. Constrained and stabilizing stacked adaptive dynamic programming and a comparison with model predictive control. \textit{2018 European control conference (ECC)}, 1349-1354, 2018. (15 цитирований)

\item \textbf{P. Osinenko}, L. Beckenbach, S. Streif. Practical sample-and-hold stabilization of nonlinear systems under approximate optimizers. \textit{IEEE Control Systems Letters}, 2 (4), 569-574, 2018. (12 цитирований)

\item L. Beckenbach, \textbf{P. Osinenko}, S. Streif. Addressing infinite-horizon optimization in MPC via Q-learning. \textit{IFAC-PapersOnLine}, 51 (20), 60-65, 2018. (12 цитирований)

\item P. Schmidt, \textbf{P. Osinenko}, S. Streif. On inf-convolution-based robust practical stabilization under computational uncertainty. \textit{IEEE Transactions on Automatic Control}, 66 (11), 5530-5537, 2021. (10 цитирований)

\item \textbf{P. Osinenko}, T. Göhrt, G. Devadze, S. Streif. Stacked adaptive dynamic programming with unknown system model. \textit{IFAC-PapersOnLine}, 50 (1), 4150-4155, 2017. (10 цитирований)

\item \textbf{P. Osinenko}, G. Devadze, S. Streif. Constructive analysis of control system stability. \textit{IFAC-PapersOnLine}, 50 (1), 7467-7474, 2017. (10 цитирований)

\item A. Morozov, M. Pugach, A. Polyakov, \textbf{P. Osinenko}, A. Bolychev, V. Terzija, et al. Optimal flow factor determination in vanadium redox flow battery control. \textit{IEEE Access}, 12, 19277-19284, 2024. (9 цитирований)

\item \textbf{P. Osinenko}, G. Yaremenko, G. Malaniya. On Stochastic Stabilization via Nonsmooth Control Lyapunov Functions. \textit{IEEE Transactions on Automatic Control}, 68 (8), 4925-4931, 2022. (9 цитирований)

\item \textbf{P. Osinenko}. Optimal slip control for tractors with feedback of drive torque. 2015. (9 цитирований)

\item \textbf{P. Osinenko}, M. Geissler, T. Herlitzius. Adaptive unscented Kalman filter with a fuzzy supervisor for electrified drive train tractors. \textit{Fuzzy Systems (FUZZ-IEEE), 2014 IEEE International Conference on}, 322-331, 2014. (9 цитирований)

\item \textbf{П. Осиненко}. Совершенствование методики обработки данных полевых испытаний наземных транспортных средств. \textit{Тракторы и сельхозмашины}, 7, 19--22, 2011. (9 цитирований)

\item \textbf{P. Osinenko}, D. Dobriborsci. Effects of sampling and prediction horizon in reinforcement learning. \textit{IEEE Access}, 9, 127611-127618, 2021. (8 цитирований)

\end{enumerate}

% Продолжение списка публикаций...
% (остальные статьи можно добавить аналогично)

\end{document}
